Concurrent Programming with CXL

### 2020-06-26 book/paper.tex
Renamed NULL to None

The list has two ``book-end'' nodes with values \texttt{-inf} and
\texttt{inf} (like the Python \texttt{math.inf} constants).
Each node has a lock, a value, and \texttt{next}, a pointer to the next node
(which is \texttt{NULL} for the final \texttt{inf} node).
The \texttt{lst\_find(lst, v)} method is a helper function for update
methods that
finds and locks two consecutive nodes \texttt{before} and \texttt{after}
such that \texttt{before.value $<$ v $\le$ after.value}.
It does so by performing something called \emph{hand-over-hand locking}.
\index{hand-over-hand locking}
It first locks the first node, which is the \texttt{-inf} node.
Then, iteratively, it obtains a lock on the next node and release the
lock on the last one, and so on, similar to climbing a tree
hand-over-hand.

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
Boolean & \texttt{False}, \texttt{True} \\
\hline
integers & \texttt{-inf, ..., -2, -1, 0, 1, 2, ..., inf} \\
\hline
Atom & \texttt{.example}, \texttt{.test1} \\
\hline
Program Counter & (method names are program counter constants) \\
\hline
Dictionary & \texttt{dict\{ .account: 12345, .valid: False \} } \\
\hline
Set & \texttt{\{ 1, 2, 3 \}, \{ False, .id, 3 \} } \\
\hline
Address & \texttt{\&lock, \&flags[2], NULL} \\
\hline
Context & (generated by \texttt{stop} expression) \\
\hline
\end{tabular}
\vspace{1em}

@@

\begin{itemize}
\item \texttt{False < True};
\item integers are ordered in the natural way;
\item atoms are lexicographically ordered;
\item program counters are ordered by their integer values;
\item dictionaries are first converted into a list of ordered (key, value)
pairs.  Then two dictionaries are lexicographically ordered by this
representation;
\item a set is first converted into an ordered list, then lexicographically
ordered;
\item an address is a list of atoms.  \texttt{NULL} is the empty list of atoms.
Addresses are lexicographically ordered accordingly;
\item contexts (Appendix~\ref{app:context}) are ordered by hash.
\end{itemize}

@@

The usage is similar to \texttt{malloc} and \texttt{free} in C.
CXL also supports an address value \texttt{NULL} that can be
used as a null pointer.  \texttt{recAlloc} returns \texttt{NULL}
when running out of memory.

>>>>

The list has two ``book-end'' nodes with values \texttt{-inf} and
\texttt{inf} (like the Python \texttt{math.inf} constants).
Each node has a lock, a value, and \texttt{next}, a pointer to the next node
(which is \texttt{None} for the final \texttt{inf} node).
The \texttt{lst\_find(lst, v)} method is a helper function for update
methods that
finds and locks two consecutive nodes \texttt{before} and \texttt{after}
such that \texttt{before.value $<$ v $\le$ after.value}.
It does so by performing something called \emph{hand-over-hand locking}.
\index{hand-over-hand locking}
It first locks the first node, which is the \texttt{-inf} node.
Then, iteratively, it obtains a lock on the next node and release the
lock on the last one, and so on, similar to climbing a tree
hand-over-hand.

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
Boolean & \texttt{False}, \texttt{True} \\
\hline
integers & \texttt{-inf, ..., -2, -1, 0, 1, 2, ..., inf} \\
\hline
Atom & \texttt{.example}, \texttt{.test1} \\
\hline
Program Counter & (method names are program counter constants) \\
\hline
Dictionary & \texttt{dict\{ .account: 12345, .valid: False \} } \\
\hline
Set & \texttt{\{ 1, 2, 3 \}, \{ False, .id, 3 \} } \\
\hline
Address & \texttt{\&lock, \&flags[2], None} \\
\hline
Context & (generated by \texttt{stop} expression) \\
\hline
\end{tabular}
\vspace{1em}

@@

\begin{itemize}
\item \texttt{False < True};
\item integers are ordered in the natural way;
\item atoms are lexicographically ordered;
\item program counters are ordered by their integer values;
\item dictionaries are first converted into a list of ordered (key, value)
pairs.  Then two dictionaries are lexicographically ordered by this
representation;
\item a set is first converted into an ordered list, then lexicographically
ordered;
\item an address is a list of atoms.  \texttt{None} is the empty list of atoms.
Addresses are lexicographically ordered accordingly;
\item contexts (Appendix~\ref{app:context}) are ordered by hash.
\end{itemize}

@@

The usage is similar to \texttt{malloc} and \texttt{free} in C.
\texttt{recAlloc} returns \texttt{None} when running out of memory.
